R Notebook

### 2021-11-06 01_studies/01_Laborstudie ProVisioNET/Fitbit/FitBit Project/Pupil_dial.Rmd
pupil dial

needs(tidyverse,
      lubridate,
      hms)
```

@@

```{r, message=FALSE, include=FALSE, error=FALSE}
part <- read_xlsx(path = "Data/Heart Rate.xlsx")

@@

assign(name3,
       value = df)  
}

@@

```{r}
df_compl <- 
  mget(ls(pattern = "tib")) %>%
  bind_rows() %>%
  mutate(ID = as_factor(ID))
```

```{r}
ggplot(data = df_compl,
       mapping = aes(x = `Heart Rate`,
                     y = dia_right
                     )
       ) +
  geom_point()
```

>>>>

needs(tidyverse,
      lubridate,
      hms,
      readxl)
```

@@

```{r, message=FALSE, include=FALSE, error=FALSE, }
part <- read_xlsx(path = "Data/Heart Rate.xlsx")

@@

df <- df %>% mutate(dia_left = scale(dia_left),
                    dia_right = scale(dia_right),
                    `Heart Rate` = scale(`Heart Rate`)
                    )
assign(name3,
       value = df)  
}

@@

```{r}
df_compl <- 
  mget(ls(pattern = "tib")) %>%
  bind_rows() %>%
  mutate(ID = as_factor(ID),
         Type = as_factor(ifelse(test = as.numeric(as.character(ID)) > 200,
                                 yes = "advanced",
                                 no = "novice"
                                 )
                          )
         )
```

```{r}
ggplot(data = na.omit(df_compl),
       mapping = aes(x = dia_right,
                     y = `Heart Rate`
                     )
       ) +
  geom_point(mapping = aes(color = as_factor(Type))) +
  geom_smooth(method = "lm")

ggplot(data = na.omit(df_compl),
       mapping = aes(x = dia_left,
                     y = `Heart Rate`
                     )
       ) +
  geom_point(mapping = aes(color = as_factor(Type))) +
  geom_smooth(method = "lm")

ggplot(data = na.omit(df_compl)
       ) + 
  geom_histogram(mapping = aes(x = dia_left),
                 alpha = 0.4,
                 color = "blue") +
  geom_histogram(mapping = aes(x = dia_right),
                 alpha = 0.4,
                 color = "red")
